---
title: "R Notebook"
output: html_notebook
---
#Statistics 14 Homework Ch20_Textbook
##20.27
###a
```{r}
#data processing
data1 <- read.csv("Xr20-27.csv",header = 1)
period1 <- data1$Period
quarter1 <- data1$Quarter
subscribers1 <- data1$Subscribers
n <- length(subscribers1)

plot(period1, subscribers1, col = "red", main = "Subscribers against Period", xlab = "period", ylab = "subscribers", xlim=range(period1), ylim=range(subscribers1))
lines(period1, subscribers1, type="o", col = "red")
```

###b
1. Centered moving average
```{r}
Center_Moving_Average <- function(x, q, s) {
   k <- length(x)
   y <- vector("double", length = k)
   SE <- vector("double", length = k)
   SI <- vector("double", length = s)
   if(s %% 2 == 0){
      lb = s / 2
      lb2 = lb + 1
      ub = k - (s / 2)
      cmv_y <- vector("double", length = k)
      for(i in lb:ub) {
         sum_x = 0
         lb_cmv = i - lb + 1
         ub_cmv = i + lb
         for(j in lb_cmv:ub_cmv){
            sum_x <- sum_x + x[j]
         }
         cmv_y[i] <- sum_x / s
      }
      for(i in lb2:ub) {
         y[i] <- (cmv_y[i-1] + cmv_y[i]) / 2
         SE[i] <- x[i] / y[i]
         SI[q[i]] <- SI[q[i]] + SE[i]
      }
      SI <- SI / ((k / s) - 1)
      sum_SI <- sum(SI)
      SI <- SI * s / sum_SI
   } else {
   lb = ceiling(s / 2) 
   ub = k - floor(s / 2)
   for(i in lb:ub) {
      sum_x = 0
      lb_cmv = i - lb + 1
      ub_cmv = i + lb - 1
      for(j in lb_cmv:ub_cmv){
         sum_x <- sum_x + x[j]
      }
      y[i] <- sum_x / s
      SE[i] <- x[i] / y[i]
      SI[q[i]] <- SI[q[i]] + SE[i]
   }
   SI <- SI / ((k / s) - 1)
   sum_SI <- sum(SI)
   SI <- SI * s / sum_SI
}
return(SI)
}
Forecast_by_SI <- function(x, q, s, SI, t) {
   k <- length(x)
   Des_x <- vector("double", length = k)
   for(i in 1:k) {
      Des_x[i] <- x[i] / SI[q[i]]
   } 
   linearModelVar <- lm(Des_x ~ t)
   b0 <- coef(linearModelVar)[1]
   b1 <- coef(linearModelVar)[2]
   new_k <- k + s
   new_lb <- k + 1
   Q_t <- vector("double", length = new_k)
   SI_Q_t <- vector("double", length = new_k)
   for(i in 1:k) {
      Q_t[i] <- q[i]
   }
   for(j in new_lb:new_k) {
      Q_t[j] <- j - k
   }
   for(i in 1:new_k) {
      SI_Q_t[i] <- SI[Q_t[i]]
   }
   F_t <- 0:(new_k - 1)
   des_y <- b0 + b1 * F_t
   y <- des_y * SI_Q_t
   plot(t, x, col = "blue", main = "Subscribers against period", xlab = "period", ylab = "x", xlim=range(t, F_t, new_k), ylim=range(x, Des_x, des_y, y, 0))
	lines(t, x, type="o", col = "blue")
	lines(t, Des_x, type="o", col = "red")
	lines(F_t, des_y, type="o", col = "green")
	lines(F_t, y, type="o", col = "black")

   return(y)
}
```

```{r}
n <- length(subscribers1)
Season <- max(quarter1)
CMV_SI <- Center_Moving_Average(subscribers1, quarter1, Season)
cat("# # # # The Centered moving average seasonal index # # # ","\n")
print(CMV_SI)
Subscribers_y_1 <- Forecast_by_SI(subscribers1, quarter1, Season, CMV_SI, period1)
cat(" ","\n")
cat("# # # # The Subscribers_y # # # ","\n")
print(Subscribers_y_1)
```

2. Linear regression
```{r}
Linear_Regression_Seasonal_Index <- function(x, q, s) {
   k <- length(x)
   SE <- vector("double", length = k)
   SI <- vector("double", length = s)
   t <- 0:(k - 1)
   linearModelVar <- lm(x ~ t)
   b0 <- coef(linearModelVar)[1]
   b1 <- coef(linearModelVar)[2]
   y <- b0 + b1 * t
   for(i in 1:k) {
      SE[i] <- x[i] / y[i]
      SI[q[i]] <- SI[q[i]] + SE[i]
   }
   SI <- SI / ((k / s) - 1)
   sum_SI <- sum(SI)
   SI <- SI * s / sum_SI
   return(SI)
}
```

```{r}
n <- length(subscribers1)
Season <- max(quarter1)
SLR_SI <- Linear_Regression_Seasonal_Index(subscribers1, quarter1, Season)
cat("# # # # The Simple Linear_Regression seasonal index # # # ","\n")
print(SLR_SI)
cat(" ","\n")
Subscribers_y_2 <- Forecast_by_SI(subscribers1, quarter1, Season, SLR_SI, period1)
cat("# # # # The Subscribers_y # # # ","\n")
print(Subscribers_y_2)
```

3. Dummy variable
```{r}
n <- length(subscribers1)
Season <- max(quarter1)
#
Dummy_I <- Season - 1
Q <- matrix(nrow =n, ncol = Dummy_I)
Dummy_Name <- vector("character", length = Dummy_I)
for(i in 1:Dummy_I){
  Dummy_Name[i] <- paste0("Q", i)
}
colnames(Q) <- Dummy_Name
for(i in 1:n){
  for(j in 1:Dummy_I){
    if(quarter1[i] == j){
      Q[i,j] <- 1
    } else {
      Q[i,j] <- 0
    }  
  }
}
#
Data.Subscribers <- cbind(period1, Q)
linearModelVar <- lm(subscribers1 ~ Data.Subscribers)
cat(" ","\n")
cat("# # # # The regression model # # # ","\n")
print(summary(linearModelVar))
cat(" ","\n")
ANOVA_T_lm <- anova(linearModelVar)
cat("# # # # The ANOVA Table # # # ","\n")
print(ANOVA_T_lm)
NoB <- Dummy_I + 2
bi <- vector("double", length = NoB)
for(i in 1:NoB){
  bi[i] <- coef(linearModelVar)[i]
}
b0 <- vector("double", length = n)
for(j in 1:n) {
    b0[j] <- 1
}
Data.Subscribers_0 <- cbind(b0, Data.Subscribers)
y_Dummy <- c(Data.Subscribers_0 %*% bi)
cat(" ","\n")
cat("# # # # The Subscribers_y # # # ","\n")
print(y_Dummy)

```

```{r}
Mean_Absolute_Deviation <- function(x, y, s) {
   k <- length(x)
   Sum_E <- 0
   for(i in s:k) {
      Sum_E <- Sum_E + abs(x[i] - y[i])
   }
   MAD <- Sum_E / (k - s + 1)
   return(MAD)
}
Mean_Square_Error <- function(x, y, s) {
   k <- length(x)
   Sum_E <- 0
   for(i in s:k) {
      Sum_E <- Sum_E + (x[i] - y[i])^2
   }
   MSE <- Sum_E / (k - s + 1)
   return(MSE)
}
Mean_Absolute_Percentage_Error <- function(x, y, s) {
   k <- length(x)
   Sum_E <- 0
   for(i in s:k) {
      if(x[i] != 0) {
         Sum_E <- Sum_E + abs(x[i] - y[i])/x[i]
      } else {
         Sum_E <- Sum_E + abs(x[i] - y[i])/mean(x)
         }	
     }
   MAPE <- Sum_E / (k - s + 1) * 100
   return(MAPE)
}
```

```{r}
CMV_MAD <- Mean_Absolute_Deviation(subscribers1, Subscribers_y_1, 4)
CMV_MSE <- Mean_Square_Error(subscribers1, Subscribers_y_1, 4)
CMV_MAPE <- Mean_Absolute_Percentage_Error(subscribers1, Subscribers_y_1, 4)
SLR_MAD <- Mean_Absolute_Deviation(subscribers1, Subscribers_y_2, 4)
SLR_MSE <- Mean_Square_Error(subscribers1, Subscribers_y_2, 4)
SLR_MAPE <- Mean_Absolute_Percentage_Error(subscribers1, Subscribers_y_2, 4)
DUM_MAD <- Mean_Absolute_Deviation(subscribers1, y_Dummy, 4)
DUM_MSE <- Mean_Square_Error(subscribers1, y_Dummy, 4)
DUM_MAPE <- Mean_Absolute_Percentage_Error(subscribers1, y_Dummy, 4)
Error_M <- matrix(nrow = 3, ncol = 3)
colnames(Error_M) = c("CMV", "SLR", "Dummy")
rownames(Error_M) = c("MAD", "MSE", "MAPE")
Error_M[1,1] <- CMV_MAD
Error_M[1,2] <- SLR_MAD
Error_M[1,3] <- DUM_MAD
Error_M[2,1] <- CMV_MSE
Error_M[2,2] <- SLR_MSE
Error_M[2,3] <- DUM_MSE
Error_M[3,1] <- CMV_MAPE
Error_M[3,2] <- SLR_MAPE
Error_M[3,3] <- DUM_MAPE
cat("     ","\n")
cat("# # # # Error Metrix # # # ","\n")
print(Error_M)
```

From the printout, the best forecast method for this problem is Dummy.

##20.47

```{r}
#data processing
data2 <- read.csv("Xr20-47.csv",header = 1)
year <- data2$Year
period <- data2$Period
quarter <- data2$Quarter
revenues <- data2$Revenues

n <- length(revenues)
plot(period, revenues, col = "red", main = "Revenues against Period", xlab = "period", ylab = "revenues", xlim=range(period), ylim=range(revenues))
lines(period, revenues, type="o", col = "red")
```
```{r}
#myts <- ts(revenues, start=c(year[1], 1), end=c(year[n], 4), frequency=4)
#plot(myts, xaxt = "n", col = "blue", main = "Revenues against Year", xlab = "Year.Quarter", ylab = "Revenues(in $millions)")
#tsp = attributes(myts)$tsp

#year_quarter = seq(as.Date("2012-01-Q1"), by = "quarter", along = myts)
#axis(1, at = seq(tsp[1], tsp[2], along = myts), labels = format(year_quarter, "%Y-%m"))

```

##20.48
Because there's seasonal effect. The seasonal component of the time-series exhibits a short term calendar repetitive behavior.
Since exponential smoothing does not consider this effect, it's not a recommended method.

##20.49

$$
y = \beta_0+\beta_1t+\varepsilon
$$
$y$ = revenues(in $millions)

$t$ = period

$\varepsilon$ = error variable

```{r}
n <- length(revenues)
period2 <- vector("integer",length = n)
for(i in 1:n)
{
  period2[i] <- period[i]-1
}
linearModelVar <- lm(revenues ~ period2)
print(summary(linearModelVar))
```

$$
\hat{y} = 20.943+0.732t
$$

##20.50
Use centered moving averages mothod to do this.

```{r}
n <- length(revenues)
Season <- max(quarter)
CMV_SI <- Center_Moving_Average(revenues, quarter, Season)
cat("# # # # The Centered moving average seasonal index # # # ","\n")
print(CMV_SI)
```

##20.51
```{r}
Revenues_y <- Forecast_by_SI(revenues, quarter, Season, CMV_SI, period2)
cat("# # # # The Revenues_y # # # ","\n")
print(Revenues_y)
```





