---
title: "R Notebook"
output: html_notebook
---

#Statistics XIII Homework Ch20_Textbook
##20.01
```{r}
#data processing
data1 <- read.csv("Xr20-01.csv",header = 1)
timeseries1 <- data1$Time.series

#line chart
n <- length(timeseries1)
period1 <- vector("integer",length = n)
for(i in 1:n)
{
  period1[i] <- i-1
}
plot(period1, timeseries1, col = "green", main = "Time Series against Period", xlab = "period", ylab = "time series", xlim=range(period1), ylim=range(timeseries1))
lines(period1, timeseries1, type="o")
abline(lm(timeseries1 ~ period1), col = "green")

```

```{r}
Moving_Average <- function(x, n) {
   k <- length(x)
   y <- vector("double", length = k + 1)
   lb = n + 1
   ub = k + 1
   for(i in lb:ub) {
       sum_x = 0
      lb_mv = i - n
      ub_mv = i - 1
      for(j in lb_mv:ub_mv){
         sum_x <- sum_x + x[j]
         }
      y[i] <- sum_x / n
   }
   return(y)
}
n <- length(timeseries1)
MV_y <- Moving_Average(timeseries1, 3)
MV_y[MV_y == 0] <- NA
plot(period1, timeseries1, col = "red", main = "Time Series against Period", xlab = "period", ylab = "time series")
lines(period1, timeseries1, type="o", col = "blue")
lines(MV_y, type="o", col = "red")
cat("####3-period moving averages results####","\n")
print(MV_y)
```

From the printout, we can forecast that the time series of the next period is 39.66667.

##20.7
```{r}
#data processing
data2 <- read.csv("Xr20-07.csv",header = 1)
timeseries2 <- data2$Time.series

#line chart
n <- length(timeseries2)
period2 <- vector("integer",length = n)
for(i in 1:n)
{
  period2[i] <- i-1
}
plot(period2, timeseries2, col = "green", main = "Time Series against Period", xlab = "period", ylab = "time series", xlim=range(period2), ylim=range(timeseries2))
lines(period2, timeseries2, type="o")
abline(lm(timeseries2 ~ period2), col = "green")
```

```{r}
n <- length(timeseries2)
Exponential_Smoothing <- function(x, a) {
   k <- length(x)
   y <- vector("double", length = k + 1)
   y[1] = x[1]
   ub_es = k+1
   for(i in 2:ub_es) {
      j <- i - 1
      y[i] <- a * x[j] + (1-a) * y[j]
   }
   return(y)
}

ES_y <- Exponential_Smoothing(timeseries2, 0.1)
ES_y[ES_y == 0] <- NA
plot(period2, timeseries2, col = "red", main = "Time Series against Period", xlab = "period", ylab = "time series")
lines(period2, timeseries2, type="o", col = "blue")
lines(ES_y, type="o", col = "red")

cat("####exponential smoothing####","\n")
print(ES_y)
```

From the printout, we can forecast that the time series of the next period is 16.51171.

##EST
###For 20.1
Apply EST with $\alpha$  = 0.8 and $\beta$ = 0.2.($F_0$ = $Y_0$ = 42, $ET_0$ = 1)
```{r}
Exponential_Smoothing_with_Trend <- function(x, a, b, f, l) {
   k <- length(x)
   y <- vector("double", length = k + 1)
   LT <- vector("double", length = k + 1)
   ET <- vector("double", length = k + 1)
   y[1] <- f + l
   LT[1] <- a * (x[1] - f) + (1-a) * (y[1] - f)
   ET[1] <- b * LT[1] + (1-b) * l
   ub_es = k + 1
   for(i in 2:k) {
      j <- i - 1
      y[i] <- a * x[j] + (1-a) * y[j] + ET[j]
      LT[i] <- a * (x[i] - x[j]) + (1-a) * (y[i] - y[j])
      ET[i] <- b * LT[i] + (1-b) * ET[j]
   }
   y[ub_es] <- a * x[k] + (1-a) * y[k] + ET[k]
   return(y)
}
n <- length(timeseries1)
EST_y <- Exponential_Smoothing_with_Trend(timeseries1, 0.8, 0.2, 42, 1)
EST_y[EST_y == 0] <- NA

plot(period1, timeseries1, col = "red", main = "Time Series against Period", xlab = "period", ylab = "time series")
lines(period1, timeseries1, type="o", col = "blue")
lines(EST_y, type="o", col = "red")
cat("# # # # The Exponential Smoothing with Trend results # # # ","\n")
print(EST_y)

```

From the printout, we can forecast that the time series of the next period is 30.15460.

###For 20.7
Apply EST with $\alpha$  = 0.8 and $\beta$ = 0.2.($F_0$ = $Y_0$ = 18, $ET_0$ = 2)
```{r}
n <- length(timeseries2)
EST_y <- Exponential_Smoothing_with_Trend(timeseries2, 0.8, 0.2, 18, 2)
EST_y[EST_y == 0] <- NA

plot(period2, timeseries2, col = "red", main = "Time Series against Period", xlab = "period", ylab = "time series")
lines(period2, timeseries2, type="o", col = "blue")
lines(EST_y, type="o", col = "red")
cat("# # # # The Exponential Smoothing with Trend results # # # ","\n")
print(EST_y)
```

From the printout, we can forecast that the time series of the next period is 15.33831.

##Compare 3 results
###For 20.1
```{r}
Mean_Absolute_Deviation <- function(x, y, s) {
   k <- length(x)
   Sum_E <- 0
   for(i in s:k) {
      Sum_E <- Sum_E + abs(x[i] - y[i])
   }
   MAD <- Sum_E / (k - s + 1)
   return(MAD)
}
Mean_Square_Error <- function(x, y, s) {
   k <- length(x)
   Sum_E <- 0
   for(i in s:k) {
      Sum_E <- Sum_E + (x[i] - y[i])^2
   }
   MSE <- Sum_E / (k - s + 1)
   return(MSE)
}
Mean_Absolute_Percentage_Error <- function(x, y, s) {
   k <- length(x)
   Sum_E <- 0
   for(i in s:k) {
      if(x[i] != 0) {
         Sum_E <- Sum_E + abs(x[i] - y[i])/x[i]
      } else {
         Sum_E <- Sum_E + abs(x[i] - y[i])/mean(x)
         }	
     }
   MAPE <- Sum_E / (k - s + 1) * 100
   return(MAPE)
}
###
MV_y <- Moving_Average(timeseries1, 3)
ES_y <- Exponential_Smoothing(timeseries1, 0.8)
EST_y <- Exponential_Smoothing_with_Trend(timeseries1, 0.8, 0.2, 42, 1)
###
MV_MAD <- Mean_Absolute_Deviation(timeseries1, MV_y, 4)
MV_MSE <- Mean_Square_Error(timeseries1, MV_y, 4)
MV_MAPE <- Mean_Absolute_Percentage_Error(timeseries1, MV_y, 4)
ES_MAD <- Mean_Absolute_Deviation(timeseries1, ES_y, 4)
ES_MSE <- Mean_Square_Error(timeseries1, ES_y, 4)
ES_MAPE <- Mean_Absolute_Percentage_Error(timeseries1, ES_y, 4)
EST_MAD <- Mean_Absolute_Deviation(timeseries1, EST_y, 4)
EST_MSE <- Mean_Square_Error(timeseries1, EST_y, 4)
EST_MAPE <- Mean_Absolute_Percentage_Error(timeseries1, EST_y, 4)
Error_M <- matrix(nrow = 3, ncol = 3)
colnames(Error_M) = c("3-MA", "ES", "EST")
rownames(Error_M) = c("MAD", "MSE", "MAPE")
Error_M[1,1] <- MV_MAD
Error_M[1,2] <- ES_MAD
Error_M[1,3] <- EST_MAD
Error_M[2,1] <- MV_MSE
Error_M[2,2] <- ES_MSE
Error_M[2,3] <- EST_MSE
Error_M[3,1] <- MV_MAPE
Error_M[3,2] <- ES_MAPE
Error_M[3,3] <- EST_MAPE
cat("     ","\n")
cat("# # # # Error Metrix # # # ","\n")
print(Error_M)
```

From the prontout, the best forecast method for 20.1 is Exponential Smoothing(0.8).

###For 20.7
```{r}
MV_y <- Moving_Average(timeseries2, 3)
ES_y <- Exponential_Smoothing(timeseries2, 0.8)
EST_y <- Exponential_Smoothing_with_Trend(timeseries2, 0.8, 0.2, 18, 2)
###
MV_MAD <- Mean_Absolute_Deviation(timeseries2, MV_y, 4)
MV_MSE <- Mean_Square_Error(timeseries2, MV_y, 4)
MV_MAPE <- Mean_Absolute_Percentage_Error(timeseries2, MV_y, 4)
ES_MAD <- Mean_Absolute_Deviation(timeseries2, ES_y, 4)
ES_MSE <- Mean_Square_Error(timeseries2, ES_y, 4)
ES_MAPE <- Mean_Absolute_Percentage_Error(timeseries2, ES_y, 4)
EST_MAD <- Mean_Absolute_Deviation(timeseries2, EST_y, 4)
EST_MSE <- Mean_Square_Error(timeseries2, EST_y, 4)
EST_MAPE <- Mean_Absolute_Percentage_Error(timeseries2, EST_y, 4)
Error_M <- matrix(nrow = 3, ncol = 3)
colnames(Error_M) = c("3-MA", "ES", "EST")
rownames(Error_M) = c("MAD", "MSE", "MAPE")
Error_M[1,1] <- MV_MAD
Error_M[1,2] <- ES_MAD
Error_M[1,3] <- EST_MAD
Error_M[2,1] <- MV_MSE
Error_M[2,2] <- ES_MSE
Error_M[2,3] <- EST_MSE
Error_M[3,1] <- MV_MAPE
Error_M[3,2] <- ES_MAPE
Error_M[3,3] <- EST_MAPE
cat("     ","\n")
cat("# # # # Error Metrix # # # ","\n")
print(Error_M)
```

From the prontout, the best forecast method for 20.7 is 3-Period Moving Averages.

