---
title: "R Notebook"
output: html_notebook
---

#Statistics III Homework Ch14_Textbook

##14.09
###a
    We want to know if there are differences in grading standards between the 4 schools.
    Hypothesis test:
$$
H_0:\mu_A=\mu_B=\mu_C=\mu_D    
$$
$$
H_1:At\ least\ two\ means\ differ.
$$


```{r}
data1 <- read.csv("Xr14-09.csv",header = 1)
nobs = nrow(data1)
df2=data.frame(y=c(data1[,1], data1[,2], data1[,3], data1[,4]),a=factor(c(rep("A", nobs), rep("B", nobs), rep("C", nobs),rep("D", nobs))))
out1=aov(y~a, data=df2)
print(summary(out1))

```
    Since p-value 0.0437 < 0.05, there is sifficient evidence to conclude that there are differences in grading standards between the 4 schools.
###b
    The required conditions for one-way ANOVA:
    1. The populations are all normally distributed.
    2. The variances of all the populations tested are equal.
    3. The observations must be independent.
    
###c
    1. Conduct Shapiro-Wilk test of normality to check if the populations are normally distributed.
    Hypothesis test:
    
$$
H_0:The\ distribution\ is\ normal.   
$$

$$
H_1:The\ distribution\ is\ not\ normal.
$$

```{r}
cat("school-A normality test:\n")
s1=shapiro.test(data1[,1])
print(s1)
cat("school-B normality test:\n")
s2=shapiro.test(data1[,2])
print(s2)
cat("school-C normality test:\n")
s3=shapiro.test(data1[,3])
print(s3)
cat("school-D normality test:\n")
s4=shapiro.test(data1[,4])
print(s4)

```
    Since p-values are all > 0.05, there is not sufficient evidence to say that the distribution is not normal.
    2. Conduct Bartlett's test to check if the variances of all the populations are equal.
    Hypothesis test:

$$
H_0:\sigma^2_1=\sigma^2_2=\sigma^2_3=\sigma^2_4    
$$

$$
H_1:At\ least\ two\ variances\ are\ different.
$$
```{r}
out2=bartlett.test(y~a, data=df2)
print(out2)
```
    Since p-value > 0.05, do not reject H0. The variances of the 4 treatments are equal.
    3. The observations must be independent.
    We know it from the question content.
    
    Thus, it appears that required conditions are satisfied.

##14.17
###a
    We want to know if the leaf sizes differ between the 3 groups.
    Hypothesis test:

$$
H_0:\mu_1=\mu_2=\mu_3    
$$

$$
H_1:At\ least\ two\ means\ differ.
$$
```{r}
data2 <- read.csv("Xr14-17.csv",header = 1)
nobs = nrow(data2)

df2=data.frame(y=c(data2[,1], data2[,2], data2[,3]),a=factor(c(rep("G1", nobs), rep("G2", nobs), rep("G3", nobs))))

out2=aov(y~a, data=df2)
print(summary(out2))

```
    Since p-value 2.84e-06 < 0.05,  there is sifficient evidence to conclude that the leaf sizes differ between the 3 groups.

###b
    We want to know if the amounts of nicotine differ in the 3 groups.
    Hypothesis test:

$$
H_0:\mu_1=\mu_2=\mu_3    
$$

$$
H_1:At\ least\ two\ means\ differ.
$$
```{r}
nobs = nrow(data2)
df3=data.frame(y=c(data2[,4], data2[,5], data2[,6]),a=factor(c(rep("G1", nobs), rep("G2", nobs), rep("G3", nobs))))

out3=aov(y~a, data=df3)
print(summary(out3))

```
    Since p-value <2e-16 < 0.05,  there is sifficient evidence to conclude that theamounts of nicotine differ in the 3 groups.

##14.21

    We want to know if there is sufficient evidence to infer that differences in commuting time exists between the 3 states.
    Hypothesis test:

$$
H_0:\mu_1=\mu_2=\mu_3    
$$

$$
H_1:At\ least\ two\ means\ differ.
$$
```{r}
data3 <- read.csv("Xr14-21.csv",header = 1)
nobs = nrow(data3)
df4=data.frame(y=c(data3[,1], data3[,2], data3[,3]),a=factor(c(rep("Cl", nobs), rep("NY", nobs), rep("Tx", nobs))))

out4=aov(y~a, data=df4)
print(summary(out4))

```
    Since p-value 3.73e-16 < 0.05,  there is sifficient evidence to infer that differences in commuting time exists between the 3 states.
