---
title: "R Notebook"
output: html_notebook
---
#Statistics II Homework Ch13_Textbook

##13.89
    We want to know if ABS is faster than non-ABS.
    We use the matched pairs hypothesis test based on the speeds.
    let μ1 = mean seconds they took to stop with ABS, μ2 = mean seconds they took to stop without ABS.

$$
H_0:\mu_1 - \mu_2 \ge 0
$$

$$
H_1:\mu_1 - \mu_2 < 0
$$

```{r}
data <- read.csv("Xr13-89.csv",header = 1)
abs <- data$ABS
non_abs <- data$non.ABS
#use built-in function
ttest1 = t.test(abs,non,alternative = "less",mu = 0,paired = TRUE,var.equal = TRUE,conf.level = 0.95)
print(ttest1)
```
    Since p-value 0.03196 < 0.05, there is sufficient evidence to infer that ABS is better.
    
##13.92
###a
    We want to know if exercise pregrams reduce medical expenses.
    We use the matched pairs hypothesis test based on the months.
    let μ1 = mean expense before programs, μ2 = mean expense after programs.

$$
H_0:\mu_1 - \mu_2 \le 0
$$

$$
H_1:\mu_1 - \mu_2 > 0
$$

```{r}
data2 <- read.csv("Xr13-92.csv",header = 1)
before <- data2$Before
after <- data2$After
#use built-in function
ttest1 = t.test(before,after,alternative = "greater",mu = 0,paired = TRUE,var.equal = TRUE,conf.level = 0.95)
print(ttest1)
```
    Since p-value 0.04842 < 0.05, there is sufficient evidence to infer that exercise pregrams reduce medical expenses.
    
###b

```{r}
ttest2 = t.test(before,after,alternative = "two.sided",mu = 0,paired = TRUE,var.equal = TRUE,conf.level = 0.95)
print(ttest2)
```
    According to the test result, the mean savings produced by exercise programs estimated with 95% is [-0.6555777, 6.8222444].
###c
    Yes. Since the medical expenses might be influenced by temperture, the samples compared in pairs based on the months can reduce the error.
    
##13.96
###a
    We want to know if the heating cost for insulated houses is less than that for the uninsulated houses.
    We use the matched pairs hypothesis test based on the sizes.
    let μ1 = mean cost for the insulated, μ2 = mean cost for the uninsulated.

$$
H_0:\mu_1 - \mu_2 \ge 0
$$

$$
H_1:\mu_1 - \mu_2 < 0
$$

```{r}
data3 <- read.csv("Xr13-96.csv",header = 1)
insulated <- data3$Insulated
uninsulated <- data3$Uninsulated
#use built-in function
ttest3 = t.test(insulated,uninsulated,alternative = "less",mu = 0,paired = TRUE,var.equal = TRUE,conf.level = 0.90)
print(ttest3)
```

    Since p-value 5.131e-11 < 0.05, there is sufficient evidence to infer that the heating cost for insulated houses is less than that for the uninsulated houses.
###b
```{r}
ttest3 = t.test(insulated,uninsulated,alternative = "two.sided",mu = 0,paired = TRUE,var.equal = TRUE,conf.level = 0.95)
print(ttest3)
```

    According to the test result, the mean savings interval due to insulating houses estimated with 95% is [50.12276,64.67724].
    
###c
    The required conditions for the paired observations case: The validity of the results depends on the normality of the differences.
    If the differences are very non-normal, we cannot use this technique.
```{r}
dif <- insulated - uninsulated
hist(dif)
```
    
    Since the difference between the two is normally distributed, we can use this technique.
##13.130
    let p1 represent the proportion of those bought extended warranty among those paid the regular price, p2 represent the proportion of those bought extended warranty among those paid the sale price.

$$
H_0:p_1 - p_2 \le 0
$$

$$
H_1:p_1 - p_2 > 0
$$

```{r}
alpha = 0.1
sum1 = 47
sum2 = 25
n1 = 229
n2 = 178
p1 = sum1/n1
p2 = sum2/n2
zcv = qnorm(alpha,lower.tail = F)
cat("z-critical value=", zcv, "\n")
p_pool = (sum1 + sum2) / (n1+n2)
sd_p_pool = sqrt(p_pool * (1-p_pool) * (1/n1 + 1/n2))
z_value = (p1 - p2) / sd_p_pool
cat("z-value=", z_value, "\n")
p_value = 1-pnorm(z_value)
cat("p-value=", p_value, "\n")

```
    Since z-value > z-critical value, we can conclude at the 10% significance level that those who paid the regular price are more likely to buy an extended warranty.
    
##13.156

    let p1 represent the proportion of (call back/religion), p2 represent the proportion of (call back/nonreligion).

$$
H_0:p_1 - p_2 \ge 0
$$

$$
H_1:p_1 - p_2 < 0
$$

```{r}
data4 <- read.csv("Xr13-156.csv",header = 1)
religion <- data4$Religion
no_religion <- data4$No.religion

religion_tab = table(religion)
nonreligion_tab = table(no_religion)

tab12 = rbind(religion_tab,nonreligion_tab)
print(tab12)
pt1 = prop.test(tab12, alternative='less', correct = FALSE)
print(pt1)
```
    Since p-value 0.07018 > 0.05, there is no sufficient evidence to infer that including a reference to religious activity reduces the probability of a call back.
    

##A13.13
###a
    We want to see if that men's choices are affected by the attractiveness of women's pictures is true. We sum the sample datas and use 2-tail method.

```{r}
data5 <- read.csv("XrA13-13.csv",header = 1)
A <- data5$Male.most
B <- data5$Male.less

A_tab = table(A)
B_tab = table(B)


tabAB = rbind(A_tab,B_tab)
print(tabAB)
pt2 = prop.test(tabAB, alternative='two.sided', correct = FALSE)
print(pt2)
```

    Since p-value 0.01837 < 0.05, there is  sufficient evidence to infer that men's choices are affected by the attractiveness of women's pictures.

###b
    We want to see if that women's choices are affected by the attractiveness of men's pictures is true. We sum the sample datas and use 2-tail method.
```{r}
C <- data5$Female.most
D <- data5$Female.less

C_tab = table(C)
D_tab = table(D)


tabCD = rbind(C_tab,D_tab)
print(tabCD)
pt3 = prop.test(tabCD, alternative='two.sided', correct = FALSE)
print(pt3)
```

    Since p-value 0.06188 > 0.05, there is  no sufficient evidence to infer that women's choices are affected by the attractiveness of men's pictures.


