---
title: "R Notebook"
output: html_notebook
---

#Statistics III Homework Ch10_Textbook

##10.5
```{r}
cat("consistency:\nif the difference between the estimator and the parameter grows smaller as the sample size grows larger, then this estimator is said to be consistent.")
```


##10.7
```{r}
cat("relative efficiency:\nif there are two or more unbiased estimators of a parameter, then the one whose variance is smaller has relative efficiency.")
```
##10.15
###a
```{r}
m = 80
zvalue = qnorm(1 - 0.05/2)
sigxbar = 5/sqrt(25)
lcl = m - zvalue*sigxbar
ucl = m + zvalue*sigxbar
cat("interval range = ",ucl-lcl,"\nThere is a 95% chance that the interval [",lcl,",",ucl,"] covers the population mean.")

```
###b
```{r}
m = 80
zvalue = qnorm(1 - 0.05/2)
sigxbar = 5/sqrt(100)
lcl = m - zvalue*sigxbar
ucl = m + zvalue*sigxbar
cat("interval range = ",ucl-lcl,"\nThere is a 95% chance that the interval [",lcl,",",ucl,"] covers the population mean.")

```
###c
```{r}
m = 80
zvalue = qnorm(1 - 0.05/2)
sigxbar = 5/sqrt(400)
lcl = m - zvalue*sigxbar
ucl = m + zvalue*sigxbar
cat("interval range = ",ucl-lcl,"\nThere is a 95% chance that the interval [",lcl,",",ucl,"] covers the population mean.")

```
###d
the confidence interval range decreases as the sample size increases.

##10.27
```{r}
rounds = c(3,41,17,1,33,37,18,15,17,12,29,51)
mr = mean(rounds)
zvalue = qnorm(1-0.05/2)
sigxbar = 12/sqrt(12)
lcl = mr - zvalue*sigxbar
ucl = mr + zvalue*sigxbar
cat("There is a 95% chance that the interval [",lcl,",",ucl,"] covers the mean number of rounds per year played by physicians.")
```
##10.35
```{r}
mcost = 1810
zvalue = qnorm(1-0.05/2)
sigxbar = 400/sqrt(64)
lcl = mcost - zvalue*sigxbar
ucl = mcost + zvalue*sigxbar
cat("There is a 95% chance that the interval [",lcl,",",ucl,"] covers the average cost of all vacations.")

```
##10.39
```{r}
data <- read.csv("Xr10-39.csv",header = 1)
times <- data$Time
mtime = mean(times)
zvalue = qnorm(1-0.05/2)
sigxbar = 1.3/sqrt(50)
lcl = mtime - zvalue*sigxbar
ucl = mtime + zvalue*sigxbar
cat("There is a 95% chance that the interval [",lcl,",",ucl,"] covers the mean assembly time for all cell phones.")
```
The interval range is narrow, which means the assembly time for the 50 cell phones tend to be concentrate.

##10.53
(do 10.51 & 10.52 first)

##10.51
###a
```{r}
zvalue = qnorm(1-0.1/2)
sd1 = 10
width = 1
n1 = (zvalue*sd1/width)^2
cat("sample size should >= ",n1,"\nwe choose 271 as our sample size.")
```
###b
```{r}
mm = 150
sigxbar = sd1/sqrt(271)
lcl = mm - zvalue*sigxbar
ucl = mm + zvalue*sigxbar
cat("sigxbar = ",sigxbar,"\ninterval range = ",ucl-lcl,"\nThere is a 90% chance that the interval [",lcl,",",ucl,"] covers the population mean.")
```
##10.52
###a
```{r}
sd2 = 5
sigxbar = sd2/sqrt(271)
lcl = mm - zvalue*sigxbar
ucl = mm + zvalue*sigxbar
cat("sigxbar = ",sigxbar,"\ninterval range = ",ucl-lcl,"\nWhen the standard deviation is 5,\nThere is a 90% chance that the interval [",lcl,",",ucl,"] covers the population mean.")

```
###b
```{r}
sd3 = 20
sigxbar = sd3/sqrt(271)
lcl = mm - zvalue*sigxbar
ucl = mm + zvalue*sigxbar
cat("sigxbar = ",sigxbar,"\ninterval range = ",ucl-lcl,"\nWhen the standard deviation is 20,\nThere is a 90% chance that the interval [",lcl,",",ucl,"] covers the population mean.")
```
##10.53
###a
the interval range is so close to 2, but a little smaller than it.

###b
then the interval range becomes smaller than that of case a, since the sigxbar is smaller.

###c
then the interval range becomes larger than that of case a, since the sigxbar is larger.

##10.55
(do 10.54 first.)

##10.54
###a
```{r}
zvalue = qnorm(1-0.05/2)
sd1 = 200
width = 10
n2 = (zvalue*sd1/width)^2
cat("sample size should >= ",n2,"\nwe choose 1537 as the sample size.")
```
###b
```{r}
mm = 500
sigxbar = sd1/sqrt(1537)
lcl = mm - zvalue*sigxbar
ucl = mm + zvalue*sigxbar
cat("sigxbar = ",sigxbar,"\ninterval range = ",ucl-lcl,"\nThere is a 95% chance that the interval [",lcl,",",ucl,"] covers the population mean.")
```
##10.55
###a
```{r}
mm = 500
sd2 = 100
sigxbar = sd2/sqrt(1537)
lcl = mm - zvalue*sigxbar
ucl = mm + zvalue*sigxbar
cat("sigxbar = ",sigxbar,"\ninterval range = ",ucl-lcl,"\nThere is a 95% chance that the interval [",lcl,",",ucl,"] covers the population mean.")
```
###b
```{r}
mm = 500
sd3 = 400
sigxbar = sd3/sqrt(1537)
lcl = mm - zvalue*sigxbar
ucl = mm + zvalue*sigxbar
cat("sigxbar = ",sigxbar,"\ninterval range = ",ucl-lcl,"\nThere is a 95% chance that the interval [",lcl,",",ucl,"] covers the population mean.")

```
From the result, we can see that the increasing of standard deviation will give a rise to sigxbar. Then it leads to the increasing of the interval range.