---
title: "R Notebook"
output: html_notebook
---
#Statistics V Homework Ch12_Textbook

##12.25
    H0:mean<=20
    H1:mean>20
    To determine if the mean > 20, we have to calculate the mean and standard deviation of samples. Also, the t critical value at 5% significant level.
```{r}
data <- read.csv("Xr12-25.csv",header = 1)
w <- data$Overweight
m1 = mean(w)
sd1 = sd(w)
n1 = nrow(data)
siglevel = .05
tcv = qt(1-siglevel,n1-1)
ucl = m1 + tcv * sd1 / sqrt(n1)
cat("mean = ",m1,"\nstd. dev.= ",sd1,"\nNumber of observation = ",n1,"\nt critical value = ",tcv,"\nucl = ",ucl)
```
    Since the sample mean(20.85 < 23.46417), we don't have sufficient evidence to reject the null hypothesis.

##12.27
    With 95% confidence level, we have to calculate [lcl,ucl], using two-tail test method.
```{r}
data <- read.csv("Xr12-27.csv",header = 1)
t <- data$Time
m2 = mean(t)
sd2 = sd(t)
n2 = nrow(data)
siglevel = .05
tcv = qt(1-siglevel/2,n2-1)
lcl = m2 - tcv * sd2 / sqrt(n2)
ucl = m2 + tcv * sd2 / sqrt(n2)
cat("mean = ",m2,"\nstd. dev.= ",sd2,"\nNumber of observation = ",n2,"\nt critical value = ",tcv,"\n[lcl,ucl] = [",lcl,ucl,"]")

```
    With 95% confidence,the mean amount of time left for all the city's meters is covered by the interval.
    
##12.75
    At a 10% significance level, we have to determine that if variance = 23. If the sample variance is upper than the chi critical value right tail or lower than the chi critical value left tail, we can say the variability has changed.
```{r}
data <- read.csv("Xr12-75.csv",header = 1)
mil <-data$Mileage
m3 = mean(mil)
sd3 = sd(mil)
v3 = var(mil)
n3 = nrow(data)
h0sd = 23
siglevel = 0.1
chistat = (n3-1)*sd3^2/h0sd^2
chicv_left = qchisq(siglevel/2,n3-1)
chicv_right = qchisq(1-siglevel/2,n3-1)
scv_left = chicv_left*h0sd^2/(n3-1)
scv_right = chicv_right*h0sd^2/(n3-1)
p_twotail = pchisq(chistat,n3-1)*2
cat("mean = ",m3,"\nstd. dev.= ",sd3,"\nvar = ",v3,"\nnumber of observation = ",n3,"\nchistat = ",chistat,"\nchi critical value left tail = ",chicv_left,"\nchi critical value right tail =",chicv_right,"\np-value(two-tail) = ",p_twotail)

```
    Since the sample variance(16.5)is higher thanchi critical value right tail(14.06714), we can say the variability has changed.
    
##12.79
    we have to estimate the population variance by the confidence interval of 90%.
```{r}
data = read.csv("Xr12-79.csv",header = 1)
o = data$Offers
m4 = mean(o)
sd4 = sd(o)
v4 = var(o)
n4 = nrow(data)
siglevel = 0.1
chicv_minusalpla = qchisq(1-siglevel/2,n4-1)
chicv_alpha = qchisq(siglevel/2,n4-1)
scv_up = (n4-1)*sd4^2/chicv_alpha
scv_down = (n4-1)*sd4^2/chicv_minusalpla
cat("mean = ",m4,"\nstd. dev.= ",sd4,"\nvar = ",v4,"\nnumber of observation = ",n4,"\ninterval = [",scv_down,",",scv_up,"]")

```

    we are 90% confidence that the interval  covers the real variance in the number of job offers made to the university's graduates.


