---
title: "R Notebook"
output: html_notebook
---
#Statistics I Homework Ch13_Textbook

##13.17
    let the variance of the weight gain using Tastee = (σ1)^2, the variance of the weight gain using product of competitor = (σ2)^2
    hypothesis:
    H0: (σ1)^2/(σ2)/2 = 1
    H1: (σ1)^2/(σ2)/2 != 1
```{r}
data <- read.csv("Xr13-17.csv",header = 1)
tast <- data$Tastee
comp <- data$Competitor
#remove NAs
tast = tast[!is.na(tast)]
ftest1=var.test(tast, comp, 
             alternative = "two.sided", conf.level = 0.95)
print(ftest1)

```
    since p-value = 0.305>0.05, there is no sufficient evidence to reject H0 at 95% confidence level. Then we apply the equal-variances t-test of μ1 – μ2.
    let μ1 is the average weight gain using Tastee, and μ2 is the average weight gain using the product of competitor.
    hypo:
    H0:μ1 - μ2 <= 0
    H1:μ1 - μ2 > 0

```{r}
ttest1 = t.test(tast, comp, alternative =  "greater", mu = 0, paired = FALSE, var.equal = TRUE, conf.level = 0.95)
print(ttest1) 
```
    since p-value is 2.227e-05< 0.05, there is sufficient evidence to reject H0 at 95% confidence level. That is, the evidence support the claim that the Tastee baby food is indeed superior.
###a
    We conclude that the Tastee baby food is indeed superior.
###b
```{r}
ttest1 = t.test(tast, comp, alternative =  "two.sided", mu = 0, paired = FALSE, var.equal = TRUE, conf.level = 0.95)
print(ttest1) 
```
    As data above, the interval with 95% confidence is[ 3.125913, 8.020754].
###c
```{r}
hist(data$Tast, main = "Weight gain after using Tastee", xlab = "weight gain")
hist(data$Comp, main = "Weight gain after using competitor's product" , xlab = "weight gain")
```
    Since both of the datasets are normally distributed, the required conditions is satisfied.
##13.33
    let the variance of the miles a new steel-belted radial tire goes = (σ1)^2, and the variance of the miles the company's current model goes = (σ2)^2
    hypothesis:
    H0: (σ1)^2/(σ2)/2 = 1
    H1: (σ1)^2/(σ2)/2 != 1
```{r}
data <- read.csv("Xr13-33.csv",header = 1)
new <- data$New
current <- data$Existing
ftest1=var.test(new, current, 
             alternative = "two.sided", conf.level = 0.95)
print(ftest1)
```
    since p-value = 0.8792>0.05, there is no sufficient evidence to reject H0 at 95% confidence level. Then we apply the equal-variances t-test of μ1 – μ2.
    let the average miles a new steel-belted radial tire goes = μ1, and the average miles the company's current model goes = μ2.
    hypothesis:
    H0:μ1 - μ2 <= 0
    H1:μ1 - μ2 > 0

```{r}
ttest1 = t.test(new, current, alternative =  "greater", mu = 0, paired = FALSE, var.equal = TRUE, conf.level = 0.95)
print(ttest1) 
```
    Since p-value = 0.1849 > 0.05, there is no sufficient evidence to reject H0 at 95% confidence level.
    That is, there is no sufficient evidence to support the claim that the new tire will last longer than the existing one.

##13.37
    let the variance of the scores before the change = (σ1)^2, and the variance of the scores after the change = (σ2)^2
    hypothesis:
    H0: (σ1)^2/(σ2)/2 = 1
    H1: (σ1)^2/(σ2)/2 != 1
```{r}
data <- read.csv("Xr13-37.csv",header = 1)
before = data$Before
after = data$After
#remove NAs
after = after[!is.na(after)]
ftest1=var.test(before, after, 
             alternative = "two.sided", conf.level = 0.95)
print(ftest1)
```
    since p-value = 0.2429>0.05, there is no sufficient evidence to reject H0 at 95% confidence level. Then we apply the equal-variances t-test of μ1 – μ2.
    let the average scores before the change = μ1, and the average scores after the change = μ2.
    hypothesis:
    H0:μ1 - μ2 >= 0
    H1:μ1 - μ2 < 0

```{r}
ttest1 = t.test(before, after, alternative =  "less", mu = 0, paired = FALSE, var.equal = TRUE, conf.level = 0.95)
print(ttest1) 
```
    Since p-value = 0.005723 < 0.05, there is sufficient evidence to reject H0 at 95% confidence level.
    That is, we can infer from the data that the SAT scores increased after the change in the school start time.

##13.116
    let the variance of the class1 = (σ1)^2, and the variance of the class2 = (σ2)^2
    hypothesis:
    H0:(σ1)^2/(σ2)^2 = 1
    H1:(σ1)^2/(σ2)^2 != 1
```{r}
data <- read.csv("Xr13-116.csv", header=1)
class1 <- data$Class.1
class2 <- data$Class.2
ftest1=var.test(class1, class2, alternative = "two.sided", conf.level = 0.95)
print(ftest1)
```
    Since p-value is 0.07835>0.05, there is no sufficient evidence to infer that the variances of the marks differ between the two sections.
##13.117
    let the variance of the week1 = (σ1)^2, and the variance of the week2 = (σ2)^2
    hypothesis:
    H0:(σ1)^2/(σ2)^2 = 1
    H1:(σ1)^2/(σ2)^2 > 1
```{r}
data <- read.csv("Xr13-117.csv", header=1)
week1 = data$Week.1
week2 = data$Week.2       
ftest1=var.test(week1, week2, alternative = "greater", conf.level = 0.95)
print(ftest1)
```
    Since p-value is 0.01832<0.05, there is  sufficient evidence to infer that limiting the minimun and maximun speeds reduces the variation in speeds.