---
title: "R Notebook"
output: html_notebook
---

#Statistics IV Homework Ch11_Textbook

##11.3
    We have to determine that if there is sufficient evidence to prove that we should play shallow, and it depends on whether the batter will hit shallow.
    H0:the batter will not hit  shallow.
    H1:the batter will hit shallow.
    so, 
    type I error:we assume the batter will hit shallow, but he/she didn't.
    type II error:we assume the batter will not hit shallow, but he/she did.
##11.5
    We have to determine that if I should land the plane immediately.
    H0:do not land
    H1:land
    Type I error:we decide to land, but there is nothing dangerous happen in 5 minutes.
    Type II error:we deicide not to land, but something dangerous happen in 5 minutes.

##11.11
    we have to determine that if there is sufficient  evidence to support that mean > 70. 
```{r}
m1 = 80
h0mean = 70
h0sd = 20
n = 100
siglevel = 0.01
zstat = (m1 - h0mean)/(h0sd/sqrt(n))
zcv_onetail = qnorm(1 - siglevel)
p_onetail= pnorm(zstat,lower.tail = FALSE)
cat("z-stat = ",zstat,"\nz critical value one tail = ",zcv_onetail,"\np-value(one-tail) = ",p_onetail,"\n")
curve(dnorm(x,h0mean,1),xlim = c(65,75),main = 'Sampling Distribution',xlab = 'sample mean',ylab = " ")
```
    since p-value < significant level, we judge the p-value to be small enough to reject that the population mean is 70.

##11.15
    H0:mean <= 7.5
    and H1:mean > 7.5
    we set the significant level = 0.05.
```{r}
m1 = 8.5
h0mean = 7.5
h0sd = 1.5
n = 30
siglevel = 0.05
zstat = (m1 - h0mean)/(h0sd/sqrt(n))
zcv_onetail = qnorm(1 - siglevel)
p_onetail= pnorm(zstat,lower.tail = FALSE)
cat("z-stat = ",zstat,"\nz critical value one tail = ",zcv_onetail,"\np-value(one-tail) = ",p_onetail,"\nwhen the significant level is 0.05.")
```
    since p-value < significant level, we judge the p-value to be small enough to infer that the mean is greater than 7.5.
##11.29
###a
    No, though that sample mean is larger than population mean, but we don't know the sample size and the population standard deviation. So the given information is not enough.
  
###b
    The p-value would be smaller than 0.5. Since we wnat to determine if the mean < 900. But the sample mean is 1050, which is much higher than 900.

##11.35
```{r}
samplem = c(15.0,15.5,16.0,16.5,17.0,17.5,18.0,18.5,19.0)
options(scripen = 999)
h0mean = 17.09
h0sd = 3.87
num = 100
cnt = 1
sigxbar = h0sd/sqrt(num)
zcv_onetail = qnorm(1-0.05)
pvalue = vector(mode = "numeric", length = 9)
for(i in 1:9)
{
  zstat = (samplem[cnt]-h0mean) / sigxbar
  pvalue[cnt]= (1-pnorm(zstat))*2
  cnt = cnt + 1
}
table<-data.frame(SampleMean=samplem,pvalue=pvalue)
table
```
##11.45
```{r}
data <- read.csv("Xr11-45.csv",header = 1)
scores <- data$GMAT
m1 = mean(scores)
truem = 560
sd0 = 50
num = 20
zvalue = qnorm(1-0.05)
sigxbar = sd0/sqrt(num)
lcl = truem - zvalue*sigxbar
ucl = truem + zvalue*sigxbar
cat("the sample mean = ",m1,"\nat the 5% significant level, if the mean of the 20 samples is in the interval[",lcl,",",ucl,"], we conclude that the dean's claim is true.")
```
    As the result, we conclude that the claim is true.
##11.55
    H0:mean <= the Titleist distances
    H1:mean > the Titleist distances
    we have to determine that if Nike's distances are farther. 
```{r}
data <- read.csv("Xr11-55.csv",header = 1)
dis <- data$Distance
m1 = mean(dis)
m = 230
sd0 = 10
num = 100
zvalue = qnorm(1-0.05)
sigxbar = sd0/sqrt(num)
ucl = m + zvalue*sigxbar
cat("the sample mean = ",m1,"\nat the 5% significant level, if the mean of the 100 samples is higher than",ucl,", we conclude that Nike is correct.")
```
    As the result, we conclude that Nike is not correct.
##11.61
```{r}
truemean = 1050
h0mean = 1000
h0sd = 50
n = 25
sigxbar = h0sd/sqrt(n)
zvalue = qnorm(1-0.01)
xc = h0mean+zvalue*sigxbar
zstat = (xc-truemean)/sigxbar
b = pnorm(zstat)
cat("reject H0 if the sample mean >",xc,"\nthe probability of a Type II error is",b)
```
