---
title: "R Notebook"
output: html_notebook
---

#Statistics XII Homework Ch18_Textbook
##18.17
###a
```{r}
#data processing
data1 <- read.csv("Xr18-17.csv",header = 1)
attendance <- data1$Attendance
yes.att <- data1$Yest.Att
I1 <- data1$I1
I2 <- data1$I2
I3 <- data1$I3
n <- length(attendance)
#
wk_u <- I1 == 1
wk_att <- attendance[wk_u]
wk_yes.att <- yes.att[wk_u]
sun_u <- I2 == 1
sun_att <- attendance[sun_u]
sun_yes.att <- yes.att[sun_u]
rain_u <- I3 == 1
rain_att <- attendance[rain_u]
rain_yes.att <- yes.att[rain_u]
#
wd_u <- I1 < 1
wd_att <- attendance[wd_u]
wd_yes.att <- yes.att[wd_u]
other_u <- (I2 < 1 & I3 < 1)
other_att <- attendance[other_u]
other_yes.att <- yes.att[other_u]
#scatter diagram_1
plot(wk_yes.att, wk_att, col = "green", main = "Attendance against The Previous Day's(weekend or not)", xlab = "previous day's att", ylab = "attendance", xlim=range(yes.att), ylim=range(attendance))
points(wd_yes.att, wd_att, col= "red")
abline(lm(wk_att ~ wk_yes.att), col = "green")
abline(lm(wd_att ~ wd_yes.att), col= "red")
#scatter diagram_2
plot(sun_yes.att, sun_att, col = "green", main = "Attendance against The Previous Day's(weather.diff)", xlab = "previous day's att", ylab = "attendance", xlim=range(yes.att), ylim=range(attendance))
points(rain_yes.att, rain_att, col= "red")
points(other_yes.att, other_att, col= "blue")
abline(lm(sun_att ~ sun_yes.att), col = "green")
abline(lm(rain_att ~ rain_yes.att), col= "red")
abline(lm(other_att ~ other_yes.att), col= "blue")
```

    Propose a statistical model:
    
$$
y\ =\ \beta_0\ +\ \beta_1x\ +\ \beta_2I_1\ +\ \beta_3I_2\ +\ \beta_4I_3\ +\ \varepsilon
$$

y = the attendance

x = the previous day's attendance

$I_1$ = day of the week (weekend = 1, else = 0)

$I_2$ = weather forecast (sunny is predicted = 1, else = 0)

$I_3$ = weather forecast (rain is predicted = 1, else = 0)

$\varepsilon$ = error variable

```{r}
attendance <- data1$Attendance
yes.att <- data1$Yest.Att
I1 <- data1$I1
I2 <- data1$I2
I3 <- data1$I3
n <- length(attendance)
Data.att <- cbind(yes.att, I1, I2, I3)
linearModelVar <- lm(attendance ~ Data.att)
cat("# # # # The regression model # # # ","\n")
print(summary(linearModelVar))
```

    From the printout, we can get the multiple regression model:

$$
\hat{y} =\ 3490.467\ + 0.369x\ +1623.096I_1\ +733.465I_2\ -765.543I_3 
$$

###b
To test the validity of the model, we use the F-test of ANOVA.

Hypothesis:

$$
H_0: \beta_1\ =\ \beta_2\ =\ \beta_3\ =\ \beta_4\ =\ 0\\
H_1: At\ least\ one\ \beta_i\ is\ not\ equal\ to\ 0.
$$

```{r}
linearModelVar <- lm(attendance ~ Data.att)
ANOVA_T_lm <- anova(linearModelVar)
cat("# # # # The ANOVA Table # # # ","\n")
print(ANOVA_T_lm)
```
Conclusion:

Since p value 9.277e-09 < 0.05, we reject $H_0$.

There is sufficient evidence to say that at least one of the $b_i$ is not equal to zero. Thus, at least one independent variable is related to y. This regression model is valid.

###c
Use t-test to test if weather is a factor in determinung attendance.

Hypothesis testing about $\beta_3$ :
    
$$
H_0:\beta_3\ =\ 0\\
H_1:\beta_3\ \neq\ 0
$$

Hypothesis testing about $\beta_4$ :
    
$$
H_0:\beta_4\ =\ 0\\
H_1:\beta_4\ \neq\ 0
$$

```{r}
linearModelVar <- lm(attendance ~ Data.att)
cat("# # # # The regression model # # # ","\n")
print(summary(linearModelVar))
```

for $\beta_3$ :

Since p-value for $I_2$ = 0.07133 > 0.05, we do not reject $H_0$.

There is NO sufficient evidence to infer that a predicted sunny day is a factor in determining attendance.

for $\beta_4$ :

Since p-value for $I_3$ = 0.12321 > 0.05, we do not reject $H_0$.

There is NO sufficient evidence to infer that a predicted rain day is a factor in determining attendance.

###Conclusion
We can not conclude that weather is a factor in determining attendance.

###d
Use t-test to test if weekend attendance is, on average, larger than weekday attendance.

Hypothesis testing about $\beta_2$ :
    
$$
H_0:\beta_2\ =\ 0\\
H_1:\beta_2\ >\ 0
$$

```{r}
linearModelVar <- lm(attendance ~ Data.att)
cat("# # # # The regression model # # # ","\n")
print(summary(linearModelVar))
```

Because we are doing right-tail test, p-value =  0.00226/2 = 0.00113
Since p-value for $I_1$ = 0.00113 < 0.05, we reject $H_0$.

There is sufficient evidence to infer that weekend attendance is, on average, larger than weekday attendance.

##18.21
###a
```{r}
#data processing
data2 <- read.csv("Xr18-21.csv",header = 1)
cost <- data2$Repairs
age <- data2$Age
machine <- data2$Machine
#
weld_u <- machine == 1
weld_cost <- cost[weld_u]
weld_age <- age[weld_u]
lathe_u <- machine == 2
lathe_cost <- cost[lathe_u]
lathe_age <- age[lathe_u]
stamp_u <- machine == 3
stamp_cost <- cost[stamp_u]
stamp_age <- age[stamp_u]

#scatter diagram
plot(weld_age, weld_cost, col = "green", main = "Cost of Repairs against Age of Machine", xlab = "Age of Machine", ylab = "Cost of Repairs", xlim=range(age), ylim=range(cost))
points(lathe_age, lathe_cost, col= "red")
points(stamp_age, stamp_cost, col= "blue")
abline(lm(weld_cost ~ weld_age), col = "green")
abline(lm(lathe_cost ~ lathe_age), col= "red")
abline(lm(stamp_cost ~ stamp_age), col= "blue")
```

    Propose a statistical model:
    
$$
y\ =\ \beta_0\ +\ \beta_1x\ +\ \beta_2I_1\ +\ \beta_3I_2\ +\ \varepsilon
$$

y = cost of repairs

x = age of machine

$I_1$ = welding machine = 1, else = 0.

$I_2$ = lathe = 1, else = 0.

if $I_1, I_2$ both = 0, then it's a stamping machine

$\varepsilon$ = error variable

```{r}
cost <- data2$Repairs
age <- data2$Age
machine <- data2$Machine
n <- length(cost)
I1 <- data2$I1
I2 <- data2$I2
for(i in 1 : n)
{
  if(machine[i] == 1)
  {
    I1[i] = 1
    I2[i]= 0
  }
  else if(machine[i] == 2)
  {
    I1[i] = 0
    I2[i] = 1
  }
  else
  {
    I1[i] = 0
    I2[i] = 0
  }
}
Data.cost <- cbind(age, I1, I2)
linearModelVar <- lm(cost ~ Data.cost)
cat("# # # # The regression model # # # ","\n")
print(summary(linearModelVar))
```

    From the printout, we can get the multiple regression model:

$$
\hat{y} =\ b_0\ +\ b_1x\ +\ b_2I_1\ +\ b_3I_2\\
=\ 119.25\ +2.54x\ -11.76I_1\ -199.37I_2
$$

###b
for $b_0$:

The intercept, b0, is 119.25.

One interpretation would be that when x, $I_1,I_2$ = 0, the cost of repairs is $119.25. 

However, we have no data for age of machine is less than 0. So, this isn’t a correct assessment.

for $b_1$:

$b_1$ = 2.54. In this model, for each additional age of machine, the cost of repairs increases on the average by 2.54 (assuming the other variables are held constant).

for $b_2$:

$b_2$ = 11.76. A welding machine, on the average, cost for $11.76 less than a stamping machine. 

for $b_3$:

$b_3$ = 199.37. A lathe, on the average, cost for $199.37 less than a stamping machine. 

###c
Use t-test to test if welding machines cost less to repair than other machines.

Hypothesis testing about $\beta_2$ :
    
$$
H_0:\beta_2\ =\ 0\\
H_1:\beta_2\ <\ 0
$$

```{r}
linearModelVar <- lm(cost ~ Data.cost)
cat("# # # # The regression model # # # ","\n")
print(summary(linearModelVar))
```

Because we are doing left-tail test, p-value = 0.55314 / 2 = 0.27657

Since p-value for $I_1$ = 0.27657 > 0.05, we  do not reject $H_0$.

There is no sufficient evidence to infer that welding machines cost less to repair than other machines.

##18.39
###a
```{r}
#data processing
data3 <- read.csv("Xr17-17.csv",header = 1)
margin <- data3$Margin
number <- data3$Number
nearest <- data3$Nearest
office <- data3$Office.Space
enrollment <- data3$Enrollment
income <- data3$Income
distance <- data3$Distance

#Scatter diagram
plot(number,margin,col="blue",main = " Margin against Number",xlab="Number of motel and hotel rooms",ylab="operating margin(in percent)")
abline(lm(margin ~ number))

plot(nearest,margin,col="blue",main = " Margin against Nearest",xlab="Number of miles to closest competition",ylab="operating margin(in percent)")
abline(lm(margin ~ nearest))

plot(office,margin,col="blue",main = " Margin against Office Space",xlab="office space in thousands of square feet",ylab="operating margin(in percent)")
abline(lm(margin ~ office))

plot(enrollment,margin,col="blue",main = " Margin against Enrollment",xlab="college and university enrollment(in thousands)",ylab="operating margin(in percent)")
abline(lm(margin ~ enrollment))

plot(income,margin,col="blue",main = " Margin against Income",xlab="medin household income(in $thousands)",ylab="operating margin(in percent)")
abline(lm(margin ~ income))

plot(distance,margin,col="blue",main = " Margin against Distance",xlab="distance(in miles) to the downtown core",ylab="operating margin(in percent)")
abline(lm(margin ~ distance))
```

```{r}
#stepwise regression
library(olsrr)
n <- length(margin)
Data.Stepwise_MG <- data.frame(cbind(number, nearest,office,enrollment,income,distance))
linearModelVar <- lm(margin ~ number + nearest + office + enrollment + income + distance, data = Data.Stepwise_MG)
cat(" ","\n")
Index_step <- ols_step_both_p(linearModelVar, details = TRUE)
print(Index_step)
```

    From the printout, we can get the regression equation:
    
$$
\hat{y}\ =\ 41.273\ +0.020*office\ -0.008*number\ +0.399*income\ +1.654*nearest
$$

```{r}
n <- length(margin)
Data.margin <- cbind(number,nearest,office,income)
linearModelVar <- lm(margin ~ Data.margin)
cat("# # # # The regression model # # # ","\n")
print(summary(linearModelVar))
ANOVA_T_lm <- anova(linearModelVar)
cat("# # # # The ANOVA Table # # # ","\n")
print(ANOVA_T_lm)
```

###b
The output produced in exercise 17.17:
```{r}
n <- length(margin)
Data.margin <- cbind(number,nearest,office,enrollment,income,distance)
linearModelVar <- lm(margin ~ Data.margin)
cat("# # # # The regression model # # # ","\n")
print(summary(linearModelVar))
ANOVA_T_lm <- anova(linearModelVar)
cat("# # # # The ANOVA Table # # # ","\n")
print(ANOVA_T_lm)
```
The stepwise regression version has less independent variables by 2, 

it has a smaller R-squared, and if we use F-test, we get a smaller p-value, which means it is more valid. 
##18.49
###a
```{r}
#data processing
data4 <- read.csv("Xr18-49.csv",header = 1)
depletion <- data4$Pct.Dep
temp <- data4$Temperature
ph <- data4$PH.Level
weather <- data4$Weather

#Scatter diagram
plot(temp,depletion,col="blue",main = " Depletion against Temperature",xlab="temperature(degree Fahrenheit)",ylab="percentage of chlorine depletion")
abline(lm(depletion ~ temp))

plot(ph,depletion,col="blue",main = " Depletion against pH Level",xlab="pH level",ylab="percentage of chlorine depletion")
abline(lm(depletion ~ ph))

plot(weather,depletion,col="blue",main = " Depletion against Weather",xlab="1=mainly cloudy, 2=sunny, 3=partly sunny",ylab="percentage of chlorine depletion")
abline(lm(depletion ~ temp))
```

1. Since it is believed that pH levels around 7.5 use the least chlorine, we use a variable to represent the diffrence between pH level of the water and 7.5.

2. We use 2 indicator variables to represent the weather variable.

The equation:

$$
y\ =\ \beta_0\ +\beta_1x_1\ +\beta_2x_2\ +\beta_3I_1\ +\beta_4I_2\ +\varepsilon
$$
y = percentage of chlorine depletion over 8 hours

$x_1$ = temperature(degree Fahrenheit)

$x_2$ = |pH level - 7.5|

$I_1$ = 1 if it is mainly cloudy, otherwise 0

$I_2$ = 1 if it is sunny, otherwise 0

if $I_1$ = $I_2$ = 0, then it is partly sunny

$\varepsilon$ = error variable

###b
```{r}
#adjustment
n <- length(depletion)
I1 <- data4$I1
I2 <- data4$I2
ph_adj <- vector("double", length = n)
for(i in 1:n)
{
  ph_adj[i] = abs(ph[i] - 7.5)
  if(weather[i] == 1)
  {
    I1[i] = 1
    I2[i] = 0
  }
  else if(weather[i] == 2)
  {
    I1[i] = 0
    I2[i] = 1
  }
  else
  {
    I1[i] = 0
    I2[i] = 0
  }
}

#regression model
Data.Depletion <- cbind(temp, ph_adj, I1,I2)
linearModelVar <- lm(depletion ~ Data.Depletion)
cat("# # # # The regression model # # # ","\n")
print(summary(linearModelVar))
```

From the printout, we can get the regression model:

$$
\hat{y}\ =\ 6.84\ +0.19x_1\ +17.18x_2\ -1.07I_1\ +1.16I_2
$$

###c
We use the F-test of ANOVA to test the validity of the model.
    Hypothesis:

$$
H_0: \beta_1\ =\ \beta_2\ =\ \beta_3\ =\ \beta_4\ =\ 0\\
H_1: At\ least\ one\ \beta_i\ is\ not\ equal\ to\ 0.
$$
```{r}
linearModelVar <- lm(depletion ~ Data.Depletion)
ANOVA_T_lm <- anova(linearModelVar)
cat("# # # # The ANOVA Table # # # ","\n")
print(ANOVA_T_lm)
```
Conclusion:

Since p value < 2.2e-16 << 0.05, we reject $H_0$.

There is sufficient evidence to say that at least one of the $b_i$ is not equal to zero. 

Thus, at least one independent variable is related to y. This regression model is valid.

###d, e, f
Use t-test to test (d), (e), (f)
```{r}
linearModelVar <- lm(depletion ~ Data.Depletion)
cat("# # # # The regression model # # # ","\n")
print(summary(linearModelVar))
```

###d
Hypothesis testing about $\beta_1$ :
    
$$
H_0:\beta_1\ =\ 0\\
H_1:\beta_1\ >\ 0
$$
for $\beta_1$ :

Because we are doing right-tail test, p-value = 2.66e-09 / 2 = 1.33e-09

Since p-value = 1.33e-09  < 0.05, we reject $H_0$.

There is sufficient evidence to infer that higher temperatures deplete chlorine more quickly.

###e
Hypothesis testing about $\beta_2$ :
    
$$
H_0:\beta_2\ =\ 0\\
H_1:\beta_2\ \neq\ 0
$$
for $\beta_2$ :

Since p-value = < 2e-16  << 0.05, we reject $H_0$.

There is sufficient evidence to infer that the belief about the relationship between chlorine depletion and pH level is correct.

###f
Hypothesis testing about $\beta_3$ :
    
$$
H_0:\beta_3\ =\ 0\\
H_1:\beta_3\ \neq\ 0
$$

for $\beta_3$ :

Since p-value = 0.1625 > 0.05, we reject $H_0$.

There is NO sufficient evidence to infer that on mainly cloudy days, the depletion of chlorine will be lower.

Hypothesis testing about $\beta_4$ :
    
$$
H_0:\beta_4\ =\ 0\\
H_1:\beta_4\ \neq\ 0
$$

for $\beta_4$ :

Since p-value = 0.1306  > 0.05, we reject $H_0$.

There is NO sufficient evidence to infer that on sunny days, the depletion of chlorine will be higher.

    Conclusion:
    
We can not infer that weather is a factor in chlorine depletion.








